Exploring location codes to work out what the Other location for deaths in NHS Borders represent

### 2021-10-19 location_code_exploration.Rmd
getting closer with the location codes now, added a data dictionary and a few more bits

@@

Note that there are too many to parse... and a lot of them are units within a hospital, which probably gets coded as a Hospital death regardless of which unit the death happeed in.

## maybe narrow it down to TD postcode - Borders LA
locations %>% filter(!institution_code_nrs %in% c(codes_hospital, codes_home, codes_care_home) & str_starts(string = postcode, pattern = "TD")) %>% print(n=nrow(.))

locations %>% filter(str_detect(string = location_name, pattern = regex("prison", ignore_case = TRUE)))

## narrow it down to Borders HB & Other locations
locations %>% 
  filter(!institution_code_nrs %in% c(codes_hospital, codes_home, codes_care_home)) %>%
  left_join(postcodes, by = "postcode") %>%
  filter(hb == "Borders") %>%
  arrange(word(location_name ,-1)) %>%
  print(n=nrow(.))

>>>>

## From data dictionary

These were provided by Evan Williams by email on 19 March 2021:

>A - Admin Office
B - Health Centre, GP Surgery
C - Clinic Premises
E - Extra-mural clinic
H - NHS Hospital
J - Joint User Hospital
K - Contractual Hospital
L - School
M - Non NHS Maternity
N - Non-Institutional, e.g. Domiciliary
P - Prison
Q - School
R - Home for the Elderly
S - Other Home
T - Miscellaneous Premises
V - Private Nursing Home, Private Hospital etc
W - School

```{r}
# datapasta::vector_paste_vertical()  # use with above list
institution_codes <-
  c("A - Admin Office",
     "B - Health Centre, GP Surgery",
     "C - Clinic Premises",
     "E - Extra-mural clinic",
     "H - NHS Hospital",
     "J - Joint User Hospital",
     "K - Contractual Hospital",
     "L - School",
     "M - Non NHS Maternity",
     "N - Non-Institutional, e.g. Domiciliary",
     "P - Prison",
     "Q - School",
     "R - Home for the Elderly",
     "S - Other Home",
     "T - Miscellaneous Premises",
     "V - Private Nursing Home, Private Hospital etc",
     "W - School") %>%
  tibble(institution_code_nrs = .) %>%
  separate(col = institution_code_nrs, into = c("institution_code_nrs","institution_type"), sep = " - ", remove = TRUE)

locations <-
  locations %>%
  left_join(institution_codes, by = "institution_code_nrs")

## any institutions without a type?
locations %>% filter(is.na(institution_type)) %>% count(institution_code_nrs)
## YES: G & Z codes don't have a type associated
```

Using the above data dictionary, we are still left with G & Z-type institutions that don't appear in the dictionary...

* `G` seems to cover clinics & medical units
* `Z` seems to cover community centres, games halls, town halls

## From NRS Covid-19 methodology paper:

@@

Note that there are too many to parse... and a lot of them are units within a hospital, which probably gets coded as a Hospital death regardless of which unit the death happened in.

```{r}
locations_hb_borders_other <-
  locations %>% 
  filter(!institution_code_nrs %in% c(codes_hospital, codes_home, codes_care_home)) %>%
  left_join(postcodes, by = "postcode") %>%
  filter(hb == "Borders")

locations_hb_borders_other %>% count(institution_code_nrs)
locations_hb_borders_other %>% filter(institution_code_nrs=="Q")

## any prisons?
locations_hb_borders_other %>% filter(str_detect(string = location_name, pattern = regex("prison|hmp", ignore_case = TRUE))) %>% print(n=nrow(.))

locations_hb_borders_other %>% filter(!str_detect(string = location_name, pattern = regex("school", ignore_case = TRUE))) %>% print(n=nrow(.))
```

## What does the first letter in the `location code` mean?

I suspect `B` is for Borders HB...

```{r}
locations_hb_borders_other %>% count(str_sub(location_code,1,1))

locations %>% anti_join(locations_hb_borders_other) %>% count(str_sub(location_code, 1, 1))

locations %>% anti_join(locations_hb_borders_other) %>% filter(str_sub(location_code, 1, 1) == "B") %>% count(is.na(postcode))

locations %>% anti_join(locations_hb_borders_other) %>% filter(str_sub(location_code, 1, 1) == "B")
```
